---
title: 'Zapotec Statistics: Praatsauce and Voicesauce'
author: "Mykel Loren Brinkerhoff"
date: "8/18/2021"
output: 
  pdf_document:
    latex_engine: xelatex
mainfont: Libertinus Serif
sansfont: Libertinus Sans
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
install.packages("tidyverse", repos = "http://cran.us.r-project.org")
install.packages("lme4", repos = "http://cran.us.r-project.org")
library(tidyverse)
library(lme4)
```
## Introduction

- This is a presentation of the statistics that I ran with my SIP interns over the summer based on Praatsauce. 
- These results are compared with the same statistics ran on data that was generated using Voicesauce


```{r data, echo=FALSE}
zapotecPS <- read.csv(file = "20210805_spectral_measures.txt")
zapotecVS <- read.table("20210816_VSOutput.txt", header = T, sep = "\t")

# Adding columns to both data frames for phonation and tone
# Adding phonation and Praatsauce output
zapotecPS$phonation <- factor(ifelse(grepl("modal", zapotecPS$Label, ignore.case = T), "Modal",
                            ifelse(grepl("breathy", zapotecPS$Label, ignore.case = T), "Breathy",
                                   ifelse(grepl("checked", zapotecPS$Label, ignore.case = T), "Checked", "Rearticulated"
                                          )
                                   )
                            ), levels = c("Modal", "Breathy", "Checked", "Rearticulated"))

zapotecPS$tone <- ifelse(grepl("_H$", zapotecPS$Label, ignore.case = F), "H",
                       ifelse(grepl("_M$", zapotecPS$Label, ignore.case = F), "M",
                              ifelse(grepl("_L$", zapotecPS$Label, ignore.case = F), "L",
                                     ifelse(grepl("_HL$", zapotecPS$Label, ignore.case = F), "HL", "MH"
                                            )
                                    )
                              )
                      )

# Adding phonation and tone to Voicesauce output 
zapotecVS$phonation <- factor(ifelse(grepl("modal", zapotecVS$Filename, ignore.case = T), "Modal",
                            ifelse(grepl("breathy", zapotecVS$Filename, ignore.case = T), "Breathy",
                                   ifelse(grepl("checked", zapotecVS$Filename, ignore.case = T), "Checked", "Rearticulated"
                                          )
                                   )
                            ), levels = c("Modal", "Breathy", "Checked", "Rearticulated"))

zapotecVS$tone <- ifelse(grepl("_H$", zapotecVS$Filename, ignore.case = F), "H",
                       ifelse(grepl("_M$", zapotecVS$Filename, ignore.case = F), "M",
                              ifelse(grepl("_L$", zapotecVS$Filename, ignore.case = F), "L",
                                     ifelse(grepl("_HL$", zapotecVS$Filename, ignore.case = F), "HL", "MH"
                                            )
                                    )
                              )
                      )


```

## Praatsauce statistics

### H1-H2
- I first plotted the results of the uncorrected and corrected values for H1-H2 by the phonation type.

```{r h1plot, echo=FALSE, fig.cap="H1-H2 uncorrected", fig.height=4, fig.width=5}
boxplot(H1H2u ~ phonation, data = zapotecPS)
```

```{r h1h2c, echo=FALSE, fig.cap="H1-H2 corrected", fig.height=4, fig.width=5}
boxplot(H1H2c ~ phonation, data = zapotecPS)

```

- Based on the above plots it does seem that there might be a difference between modal and non-modal phonation. 

- In order to test this I ran a linear regression on the uncorrected and then on the corrected. 

```{r h1h2lm, echo = FALSE}
h1u <- lm(formula = H1H2u ~ phonation,
                data = zapotecPS)
summary(h1u)
```

- Based on these results it appears as if only Breathy and Rearticulated phonation types are able to be distinguished using H1-H2.

- However the results show something different when we compare the corrected values. 

```{r h1h2clm, echo=FALSE}
h1c <- lm(formula = H1H2c ~ phonation,
                data = zapotecPS)
summary(h1c)
```

- These results show that all values can be distinguished from modal phonation using H1 - H2

- Next I ran a linear mixed effects regression with tone being a random variable. 

```{r h1h2ulmer, echo=FALSE}
uncorrected_lmer <- lmer(H1H2u ~ phonation + (1 | tone), 
               data = zapotecPS )
summary(uncorrected_lmer)
```

- Based on the t value ≥ |2| in the Fixed effects only Breathy and Rearticulated phonations are able to be distinguished from modal using this model. 

- These results differ when they are evaluated using the corrected values. We now observe that all the phonation types reach significance. 

```{r h1h2c_lmer, echo=FALSE}
corrected_lmer <- lmer(formula = H1H2c ~ phonation + (1 | tone),
                data = zapotecPS)
summary(corrected_lmer)
```
### CPP

- In turning to CPP by phonation type we see similar differences.

```{r cpp_plots, fig.cap="CPP by phonation types", fig.height=4, fig.width=5}
boxplot(CPP ~ phonation, data = zapotecPS)
```

- Looking at the results of the linear regression we see that phonation types can be differentiated using CPP. 

```{r cpp_lr}
cpp_linear <- lm(formula = CPP ~ phonation,
          data = zapotecPS)
summary(cpp_linear)
```

- These results carry over when we do a linear mixed effects regression

```{r cpp_lmer}
cpp_lmer <- lmer(CPP ~ phonation + (1 | tone), 
               data = zapotecPS )
summary(cpp_lmer)
```


## Voicesauce statistics

### H1-H2
- When we consider the results from Voicesauce the picture is somewhat different. 

```{r VS_H1Plot, fig.cap="Voicesauce H1-H2 (corrected) by phonation types", fig.height=4, fig.width=5}
boxplot(H1H2c_mean ~ phonation, data = zapotecVS)
```

```{r VS_H1PlotUn, fig.cap="Voicesauce H1-H2 (uncorrected) by phonation types", fig.height=4, fig.width=5}
boxplot(H1H2u_mean ~ phonation, data = zapotecVS)
```

- When we run the stats using a linear regression we see that checked and rearticulated phonation types are significant using H1-H2 (corrected) and only breathy is significant using H1-H2 (uncorrected).  

```{r }
h1h2_VScorrected <- lm(formula = H1H2c_mean ~ phonation,
                data = zapotecVS)
summary(h1h2_VScorrected)

h1h2_VSuncorrected <- lm(formula = H1H2u_mean ~ phonation,
                data = zapotecVS)
summary(h1h2_VSuncorrected)
```

- A linear mixed effects regression for H1-H2 (corrected) 

```{r}
h1h2c_VS <- lmer(formula = H1H2c_mean ~ phonation + (1 | tone),
                data = zapotecVS)
summary(h1h2c_VS)
```

- And H1-H2 (uncorrected)

```{r}
h1h2u_VS <- lmer(formula = H1H2u_mean ~ phonation + (1 | tone),
                data = zapotecVS)
summary(h1h2u_VS)
```

### CPP

- In turning to CPP by phonation type we do not see any clear differences between the different phonation types.

```{r cppVS_plots, fig.cap="CPP by phonation types (Voicesauce)", fig.height=4, fig.width=5}
boxplot(CPP_mean ~ phonation, data = zapotecVS)
```

- Looking at the results of the linear regression we see that phonation types cannot be differentiated using CPP. 

```{r cppVS_lr}
cppVS_linear <- lm(formula = CPP_mean ~ phonation,
          data = zapotecVS)
summary(cppVS_linear)
```

- These results carry over when we do a linear mixed effects regression

```{r cppVS_lmer}
cpp_lmer <- lmer(CPP_mean ~ phonation + (1 | tone), 
               data = zapotecVS )
summary(cpp_lmer)
```