---
title: "Handout"
author: "Mykel Loren Brinkerhoff"
date: "2022 Jan 20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(scales)
library(metan)

# custom theme for plotting
my.theme <- theme(axis.text = element_text(colour="black", size=25),
                  text = element_text(size=26),
                  title = element_text(size=29),
                  axis.title.x=  element_text(vjust=-0.45),
                  axis.title.y = element_text(vjust=.2),
                  axis.ticks = element_line(colour="black"),
                  axis.line = element_line(),
                  legend.position = c(.8,.9),
                  legend.background = element_rect(size=0.25,
                                                   linetype="solid",
                                                   color = "black"),
                  )

# Adding the csv/txt file
zapotecVS <- read.table("~/Documents/1_Projects/QP2/SLZTone.txt", header = T, sep = "\t")

# Extract the phonation and the tone labels into new
# Phonation Labels
# Add a column for the different tones  using an ifelse statement that
# greps for the different phonations
zapotecVS$phonation <- factor(ifelse(grepl("modal", zapotecVS$Filename, ignore.case = T), "Modal",
                                     ifelse(grepl("breathy", zapotecVS$Filename, ignore.case = T), "Breathy",
                                            ifelse(grepl("checked", zapotecVS$Filename, ignore.case = T), "Checked", "Laryngealized"
                                            )
                                     )
), levels = c("Modal", "Breathy", "Checked", "Laryngealized"))

# Tone Labels
# Add a column for the different tones  using an ifelse statement that
# greps for the different tones
# An example of what it is looking like
# DF$KIND <- ifelse(grepl("gas", DF$GLDESC, ignore.case = T), "Materials", 
#                   ifelse(grepl("payroll", DF$GLDESC, ignore.case = T), "Payroll", "Other"))

zapotecVS$tone <- ifelse(grepl("_H.mat", zapotecVS$Filename, ignore.case = F), "H",
                         ifelse(grepl("_M.mat", zapotecVS$Filename, ignore.case = F), "M",
                                ifelse(grepl("_L.mat", zapotecVS$Filename, ignore.case = F), "L",
                                       ifelse(grepl("_HL.mat", zapotecVS$Filename, ignore.case = F), "HL", 
                                              ifelse(grepl("_MH.mat", zapotecVS$Filename, ignore.case = F), "MH", "N"
                                       )
                                )
                         )
)
)

```

## Introduction 

- I have some preliminary results for FSRs responses. 
- I first generated a two-way table that tallies the number of occurances of tone by phonation. 
- From this we see a gap in the possible combinations of tone and phonation, which bears some stricking similarities to San Lucas Quiaviní Zapotec. 

```{r tone_phonation, echo=FALSE}
table(zapotecVS$tone, zapotecVS$phonation)
```
- This shows that SLZ only allows 
## Tonal plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
zapotec_times <- zapotecVS %>% 
  mutate(normalized_time = round((t_ms-seg_Start)/(seg_End-seg_Start),digits = 2))

# Plotting the tone
# ggplot of normalized tone (y-axis) over time (x axis)
tone_plot <- ggplot(data = zapotec_times, 
       aes(x = normalized_time, 
          y=strF0, 
          group=tone, 
          colour=tone,
          fill=tone)) +
    geom_smooth(method = "loess") +
    labs(title = "FSR's average F0 contours across tonal patterns", 
       x = "Normalized time (% of vowel duration)",
       y = "F0 (Hz)",
       colour = "Tonal Pattern") +
    theme_bw() +
    guides(colour = guide_legend("Tonal Pattern", ncol = 5), 
           fill = guide_legend("Tonal Pattern", ncol = 5) ) +
    my.theme

print(tone_plot)
```

## Moving forward

